Gammapy: A Python package for gamma-ray astronomy

### 2023-08-25 src/ms-review.tex

\author{
        Axel Donath \thanks{Mail inquiries to:
        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:28}} \and
        Régis Terrier \inst{\ref{inst:20}} \and
        Quentin Remy \inst{\ref{inst:17}} \and
        Atreyee Sinha \inst{\ref{inst:15}} \and
        Cosimo Nigro \inst{\ref{inst:24}} \and
        Fabio Pintore \inst{\ref{inst:26}} \and
        Bruno Khélifi \inst{\ref{inst:20}} \and
        Laura Olivera-Nieto \inst{\ref{inst:17}}\and
        Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
        Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
        Maximilian Linhoff \inst{\ref{inst:11}} \and
        Jose Louis {Contreras} \inst{\ref{inst:15}} \and
        Fabio Acero \inst{\ref{inst:1}} \and
        Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
        David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
        Pooja Bhattacharjee \inst{\ref{inst:8}} \and
        Johannes Buchner \inst{\ref{inst:12}} \and
        Catherine Boisson \inst{\ref{inst:9}} \and
        David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
        Andrew Chen \inst{\ref{inst:14}} \and
        Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
        Christoph Deil \inst{\ref{inst:17}} \and
        Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
        Stefan Funk \inst{\ref{inst:19}} \and
        Luca Giunti \inst{\ref{inst:20}} \and
        Jim Hinton \inst{\ref{inst:17}} \and
        Léa Jouvin \inst{\ref{inst:32}} \and
        Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
        Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
        Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
        Jean-Philippe Lenain \inst{\ref{inst:22}} \and
        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
        Lars Mohrmann \inst{\ref{inst:17}} \and
        Daniel Morcuende \inst{\ref{inst:15}} \and
        Sebastian Panny \inst{\ref{inst:25}} \and
        Maxime Regeard \inst{\ref{inst:20}} \and
        Lab Saha \inst{\ref{inst:15}} \and
        Hubert Siejkowski \inst{\ref{inst:27}} \and
        Aneta Siemiginowska \inst{\ref{inst:28}} \and
        Brigitta M. {Sipőcz} \inst{\ref{inst:29}} \and
        Tim Unbehaun \inst{\ref{inst:19}} \and
        Christopher {van Eldik} \inst{\ref{inst:19}} \and
        Thomas Vuillaume \inst{\ref{inst:8}} \and
        Roberta Zanin \inst{\ref{inst:18}}
}

\institute{
        Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:1} \and
        Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:2} \and
        Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:3} \and
        Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:4} \and
        Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:5} \and
        Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:6} \and
        Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:7} \and
        Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:8} \and
        Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:9} \and
        Point8 GmbH \label{inst:10} \and
        Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:11} \and
        Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:12} \and
        Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:13} \and
        School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:14} \and
        IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:15} \and
        The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:16} \and
        Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:17} \and
        Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:18} \and
        Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:19} \and
        Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:20} \and
        Meteo France International \label{inst:21} \and
        Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:22} \and
        Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:23} \and
        Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:24} \and
        Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:25} \and
        INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:26} \and
        Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:27} \and
        Center for Astrophysics | Harvard and Smithsonian \label{inst:28} \and
        Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:29} \and
        Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:30} \and
        Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:31} \and
        IRFU, CEA, Université Paris-Saclay, F-91191 Gif-sur-Yvette, France \label{inst:32}
}

>>>>

\author{
        Axel Donath \thanks{Mail inquiries to:
        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:001}} \and
        Régis Terrier \inst{\ref{inst:002}} \and
        Quentin Remy \inst{\ref{inst:003}} \and
        Atreyee Sinha \inst{\ref{inst:004}} \and
        Cosimo Nigro \inst{\ref{inst:005}} \and
        Fabio Pintore \inst{\ref{inst:006}} \and
        Bruno Khélifi \inst{\ref{inst:002}} \and
        Laura Olivera-Nieto \inst{\ref{inst:003}}\and
        Jose Enrique {Ruiz} \inst{\ref{inst:007}} \and
        Kai Brügge \inst{\ref{inst:008},\ref{inst:009}} \and
        Maximilian Linhoff \inst{\ref{inst:009}} \and
        Jose Louis {Contreras} \inst{\ref{inst:004}} \and
        Fabio Acero \inst{\ref{inst:010}} \and
        Arnau Aguasca-Cabot \inst{\ref{inst:011}, \ref{inst:012}, \ref{inst:013}, \ref{inst:014}} \and
        David Berge \inst{\ref{inst:015}, \ref{inst:016}} \and
        Pooja Bhattacharjee \inst{\ref{inst:017}} \and
        Johannes Buchner \inst{\ref{inst:018}} \and
        Catherine Boisson \inst{\ref{inst:019}} \and
        David {Carreto Fidalgo} \inst{\ref{inst:020}} \and
        Andrew Chen \inst{\ref{inst:021}} \and
        Mathieu {de Bony de Lavergne} \inst{\ref{inst:017}} \and
        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:022}} \and
        Christoph Deil \inst{\ref{inst:003}} \and
        Matthias Fü{\ss}ling \inst{\ref{inst:023}} \and
        Stefan Funk \inst{\ref{inst:024}} \and
        Luca Giunti \inst{\ref{inst:002}} \and
        Jim Hinton \inst{\ref{inst:003}} \and
        Léa Jouvin \inst{\ref{inst:025}} \and
        Johannes King \inst{\ref{inst:026}, \ref{inst:003}} \and
        Julien Lefaucheur \inst{\ref{inst:027}, \ref{inst:002}} \and
        Marianne Lemoine-Goumard \inst{\ref{inst:028}} \and
        Jean-Philippe Lenain \inst{\ref{inst:029}} \and
        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:007}} \and
        Lars Mohrmann \inst{\ref{inst:003}} \and
        Daniel Morcuende \inst{\ref{inst:004}} \and
        Sebastian Panny \inst{\ref{inst:032}} \and
        Maxime Regeard \inst{\ref{inst:002}} \and
        Lab Saha \inst{\ref{inst:004}} \and
        Hubert Siejkowski \inst{\ref{inst:030}} \and
        Aneta Siemiginowska \inst{\ref{inst:001}} \and
        Brigitta M. {Sipőcz} \inst{\ref{inst:031}} \and
        Tim Unbehaun \inst{\ref{inst:024}} \and
        Christopher {van Eldik} \inst{\ref{inst:024}} \and
        Thomas Vuillaume \inst{\ref{inst:017}} \and
        Roberta Zanin \inst{\ref{inst:023}}
}

\institute{
        Center for Astrophysics | Harvard and Smithsonian \label{inst:001} \and
        Université de Paris Cité, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France  \label{inst:002} \and
        Max-Planck-Institut für Kernphysik, P.O. Box 103980, D 69029 Heidelberg, Germany \label{inst:003} \and
        IPARCOS Institute and EMFTEL Department, Universidad Complutense de Madrid, E-28040 Madrid, Spain \label{inst:004} \and
        Institut de Física d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, Bellaterra, 08193 Barcelona, Spain \label{inst:005} \and
        INAF/IASF Palermo, Via U. La Malfa, 153, 90146 Palermo PA \label{inst:006} \and
        Instituto de Astrofísica de Andalucía-CSIC, Glorieta de la Astronomía s/n, 18008, Granada, Spain \label{inst:007} \and
        Point8 GmbH \label{inst:008} \and
        Astroparticle Physics, Department of Physics, TU Dortmund University, Otto-Hahn-Str. 4a, D-44227 Dortmund \label{inst:009} \and
        Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, F-91191 Gif-sur-Yvette, France \label{inst:010} \and
        Departament de Física Quàntica i Astrofísica (FQA), Universitat de Barcelona (UB),  c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:011} \and
        Institut de Ciències del Cosmos (ICCUB), Universitat de Barcelona (UB), c. Martí i Franqués, 1, 08028 Barcelona, Spain \label{inst:012} \and
        Institut d'Estudis Espacials de Catalunya (IEEC), c. Gran Capità, 2-4, 08034 Barcelona, Spain \label{inst:013} \and
        Departament de Física Quàntica i Astrofísica, Institut de Ciències del Cosmos, Universitat de Barcelona, IEEC-UB, Martí i Franquès, 1, 08028, Barcelona, Spain \label{inst:014} \and
        Deutsches Elektronen-Synchrotron (DESY), D-15738 Zeuthen, Germany \label{inst:015} \and
        Institute of physics, Humboldt-University of Berlin, D-12489 Berlin, Germany \label{inst:016} \and
        Université Savoie Mont Blanc, CNRS, Laboratoire d’Annecy de Physique des Particules - IN2P3, 74000 Annecy, France \label{inst:017} \and
        Max Planck Institute for extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany \label{inst:018} \and
        Laboratoire Univers et Théories, Observatoire de Paris, Université PSL, Université Paris Cité, CNRS, F-92190 Meudon, France \label{inst:019} \and
        Max Planck Computing and Data Facility, Gießenbachstraße 2, 85748 Garching \label{inst:020} \and
        School of Physics, University of the Witwatersrand, 1 Jan Smuts Avenue, Braamfontein, Johannesburg, 2050 South Africa \label{inst:021} \and
        The Hong Kong University of Science and Technology, Department of Electronic and Computer Engineering \label{inst:022} \and
        Cherenkov Telescope Array Observatory gGmbH (CTAO gGmbH) Saupfercheckweg 1 69117 Heidelberg \label{inst:023} \and
        Erlangen Centre for Astroparticle Physics (ECAP), Friedrich-Alexander-Universität Erlangen-Nürnberg, Nikolaus-Fiebiger Strasse 2, 91058 Erlangen, Germany \label{inst:024} \and
        IRFU, CEA, Université Paris-Saclay, F-91191 Gif-sur-Yvette, France \label{inst:025}
        Bruno-Bauer-Straße 22, 12051 Berlin  \label{inst:026} \and
        Meteo France International \label{inst:027} \and
        Université Bordeaux, CNRS, LP2I Bordeaux, UMR 5797 \label{inst:028} \and
        Sorbonne Université, Université Paris Diderot, Sorbonne Paris Cité, CNRS/IN2P3, Laboratoire de Physique Nucléaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252 Paris, France \label{inst:029} \and
        Academic Computer Centre Cyfronet, AGH University of Science and Technology, Krakow, Poland \label{inst:030} \and
        Caltech/IPAC, MC 100-22, 1200 E. California Boulevard, Pasadena, CA 91125 USA \label{inst:031} \and
        Institut für Astro- und Teilchenphysik, Leopold-Franzens-Universität Innsbruck, A-6020 Innsbruck, Austria \label{inst:032}
}
